Tailoring Differentially Private Bayesian Inference to Distance Between Distributions

### 2018-11-02 notes/fullproof/main.tex
update notes and Arixv
remove the dilation property and sliding property proof and save them into notes of SlidingDilation

\author[*]{Jiawen Liu}
\author[**]{Mark Bun}
\author[*]{Gian Pietro Farina}
\author[*]{Marco Gaboardi}
\affil[*]{Department of Computer Science and Engineering, University at Buffalo, SUNY. \{jliu223,gianpiet,gaboardi\}@buffalo.edu}
\affil[**]{Department of Computer Science, Princeton University. {mbun@cs.princeton.edu}}
\date{}
\maketitle
\section{Preliminaries}
\label{sec_background}

@@

\noindent \textbf{Differential Privacy.} 
\begin{definition}
$\epsilon-$differential privacy.

A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any adjacent\footnote{Given $\dataobs, \dataobs'$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } input $\dataobs, \dataobs' \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
\begin{equation*}
\mathbb{P}[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \mathbb{P}[H(\mathcal{M}(\dataobs')) \in B].
\end{equation*}

@@

\begin{definition}
$(\epsilon,\delta)-$differential privacy.

A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
\begin{equation*}
\mathbb{P}[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \mathbb{P}[H(\mathcal{M}(\dataobs')) \in B] + \delta,
\end{equation*}
vwhere $\dataobs = (x_i)_{i = 1}^n$ and $\dataobs = (x'_i)_{i = 1}^n$ is adjacent if there is only one $j$ that $x_j \neq x'_j$ and $x_i = x'_i$ for $i = 1, 2, \cdots, n; i \neq j$. 
\end{definition}

@@

\section{Mechanism Proposition}
\label{sec_mechs}
Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and a sequence of $n$ observations $\dataobs\in\{0,1\}^n$, we define the follwing set:
\[
  \candidateset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\},
\]
where $\Delta\alpha$ is as defined in Section\ref{sec_background}.
Notice that $\candidateset$ has $n + 1$ elements, and
the Bayesian Inference process will produce an element from $\candidateset$
that we denote by $\bysinfer(\dataobs)$ -- we don't explicitely
parametrize the result by the prior, which from now on we consider
fixed and we denote it by $\bprior$.

@@

\begin{definition}
\label{def_smoo}
The mechanism $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
\begin{equation*}
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
{\sum_{r'\in\candidateset} exp\Big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r')}{2\cdot S(\dataobs)}\Big)}.
\end{equation*}
where $S_\beta(\dataobs)$ is the smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated by:

\begin{equation}
  \label{eq:smooth}
   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{LS(\dataobs') \cdot e^{-\gamma\cdot d(\dataobs,\dataobs')}\bigg\},
\end{equation}
where $d$ is the Hamming distance between two datasets, and $\beta =
\beta(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$. 
\end{definition}

This mechanism is based on the basic exponential mechanism
\cite{talwar}, with $\candidateset$ as the range and
$\hellinger(\cdot,\cdot)$ as the scoring function. The difference is
that in this mechanism we don't calibrate the noise w.r.t. to the
global sensitivity of the scoring function but w.r.t. to the smooth
sensitivity $S(\dataobs)$ -- defined by \cite{nissim2007smooth}-- of
$\hellinger(\bysinfer(\dataobs), \cdot)$.

$\gamma = \gamma(\epsilon, \delta)$ is a function of $\epsilon$ and $\delta$ to
be determined later, and where $LS(\dataobs')$ denotes the local
sensitivity at $\bysinfer(\dataobs')$, or equivalently at $\dataobs'$,
of the scoring function used in our mechanism.

@@

By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$, $\hexpmech$ is $(\epsilon, \delta) -$differentially private, where $\delta = \frac{e^{\frac{\epsilon}{2}} \delta'}{2}$. (or $\gamma = \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$ when generalized to Dirichlet-multinomial System)

@@

\noindent \textbf{Sliding Property of $\hexpmech$}
\begin{lem}
\label{lem_sliding}
Given $\hexpmech(\dataobs)$ calibrated on the smooth sensitivity. Let $\lambda = f(\epsilon,
\delta')$, $\epsilon\geq 0$ and $|\delta'| < 1$. Then, the following \emph{sliding property} holds:
\begin{equation*}
\underset{r \thicksim \hexpmech(\dataobs)}{Pr}[u(r,\dataobs) = \hat{s}]
\leq
e^{\frac{\epsilon}{2}} \underset{r \thicksim \hexpmech(\dataobs)}{Pr}[u(r,\dataobs) = (\delta' + \hat{s})] + \frac{\delta'}{2},
\end{equation*}

\end{lem}

\begin{proof}

In what follows, we will use a correspondence between the probability
 $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$ of every
 $r\in\candidateset$ and the probability 
 $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) =
 \hellinger(\bysinfer(\dataobs),r)]$ for the utility score of $r \in \candidateset$. In Beta-binomial system, because of the property of beta function, the order of parameters in Beta distribution doesn't matter when computing the Hellinegr distance.

 \begin{thm}
 \label{thm_hellinegr_equality_beta}
 for 3 different beta distributions $\betad(\alpha_0, \beta_0)$, $\betad(\alpha_1, \beta_1)$ and $\betad(\alpha_2, \beta_2)$, $\hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_1, \beta_1)) = \hellinger(\betad(\alpha_0, \beta_0),\betad(\alpha_2, \beta_2))$ iff:
  $$
  \alpha_2 = \beta_1, \alpha_1 = \beta_2, \alpha_0 + \alpha_1 = \beta_0 + \beta_2, \alpha_0 + \alpha_2 = \beta_0 + \beta_1.
  $$
 \end{thm}

\begin{thm}
 \label{thm_hellinegr_equality_dirichlet}
 In Dirichlet-multinomial system, for 3 different Dirichlet distributions $\dirichlet(\valpha)$, $\dirichlet(\vbeta_1)$ and $\dirichlet(\vbeta_2)$, $\hellinger(\dirichlet(\valpha),\dirichlet(\vbeta_1)) = \hellinger(\dirichlet(\valpha),\dirichlet(\vbeta_2))$ iff:
  $$
  set(\vbeta_1) = set(\vbeta_2)\ and\ set(\valpha + \vbeta_1) = set(\valpha + \vbeta_2),
  $$
  where $set(\cdot)$ means we only consider the value of each dimension in the vector without the order.
 \end{thm}

 \begin{thm}
 \label{thm_candidate_divide}
 There are at most two candidates in $\candidateset$ can have the same score, i.e., for every $r \in \candidateset$, $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)]$ either 
 $$
 = 2\Big ( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]\Big )
 $$ or 
 $$
 =\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r].
 $$
 \end{thm}
 \begin{proof} of Theorem \ref{thm_candidate_divide}.

 Let $|z|$ be the number of candidates $z \in \mathcal{R}$ that satisfy $\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)$, i.e. $u(z,\dataobs) = u(r,\dataobs)$, then  $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = u(r,\dataobs)] = |z| \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.

 From Theorem \ref{thm_hellinegr_equality_beta}, It can be infer that $|z| = 2$ or $|z| = 1$, i.e., $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = u(r,x)] = 2 \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$ or $\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]$.
 \end{proof}

\begin{thm}
 \label{thm_candidate_divide_dirichlet}
 In Dirichlet-multinomial system with $k$-dimensional Dirichlet distribution, for every $r \in \candidateset$:
 $$
 \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[\hellinger(\bysinfer(\dataobs),z) = \hellinger(\bysinfer(\dataobs),r)] 
 = |z|\Big ( \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[z = r]\Big ),
 $$ 
 and $|z| = \frac{k! k!}{|a_1|! |a_2|! \cdots |a_{k_a}|! \cdot |b_1|! |b_2|! \cdots |b_{k_b}|!}$, where $\sum{|a_i|} = \sum{|b_i|} = k$.
 \end{thm}

 \begin{proof} of Theorem \ref{thm_candidate_divide_dirichlet}.

 Let $\bysinfer(\dataobs) = \dirichlet(\valpha)$, and $\dirichlet(\vbeta)$ be a candidate from $\candidateset$, 
 $a_i$ is the distinct value in $\valpha$ and $b_i$ the same in $\vbeta$, 
 $|a_i|$ denotes the number of values in $\valpha$ having the value $a_i$ and $|b_i|$ the same in $\vbeta$.
 Then, there are $\frac{k! k!}{|a_1|! |a_2|! \cdots |a_{k_a}|! \cdot |b_1|! |b_2|! \cdots |b_{k_b}|!}$ possible permutation when the condition in Theorem \ref{thm_hellinegr_equality_dirichlet} is satisfied.
 \end{proof}

 In Beta-binomial system, let $R_1, R_2 \subset \candidateset$ be a partition of $\candidateset$, where every $z \in R_1$ has a distinct score, i.e., $|z| = 1$ and $z \in R_2$ has another $z' \in R_2$ with the same score, i.e., $|z| = 2$. The proofs are given by parts:

 \begin{itemize}
 	\item for $r \in R_1$:

		We denote the normalizer of the probability mass in $\hexpmech(\dataobs)$: $\sum_{r' \in \mathcal{R}}exp(\frac{\epsilon u(r',x)}{2 S(\dataobs)})$ as $NL(\dataobs)$:
		\begin{equation*}
		\begin{split}
		LHS 
		  = \underset{r \thicksim \hexpmech(\dataobs)}{Pr}[u(r,x) = \hat{s}]
		& = \frac{exp(\frac{\epsilon \hat{s}}{2 S(\dataobs)})}{NL(\dataobs)}\\
		& = \frac{exp(\frac{\epsilon (\hat{s} + \delta' - \delta')}{2 S(\dataobs)})}{NL(\dataobs)}\\
		& = \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)} + \frac{- \epsilon \delta'}{2 S(\dataobs)})}{NL(\dataobs)}\\
		& = \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)})}.\\
		\end{split}
		\end{equation*}

		By bounding the $\delta' \geq -S(\dataobs)$, we can get:

		\begin{equation*}
		\begin{split}
		\frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{- \epsilon \delta'}{2 S(\dataobs)}}
		& \leq \frac{exp(\frac{\epsilon (\hat{s} + \delta')}{2 S(\dataobs)})}{NL(\dataobs)} \cdot e^{\frac{\epsilon}{2}}\\
		&  =  e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(r,x) = (\delta' + \hat{s})] \leq RHS\\
		\end{split}
		\end{equation*}
	\item for $r \in R_2$: Proof actually is exactly the same as above by eliminating the parameter $|z|$ in both sides.
\end{itemize}

The same in Dirichlet-multinomial distribution, partitioning the $\candidateset$ by the possible value of $|z|$, the proof can be derived in the same way as above by part.

\noindent \textbf{Dilation Property of $\hexpmech$}
\begin{lem}
\label{lem_dilation}
for any exponential mechanism $\hexpmech(\dataobs)$, $\lambda < |\beta|$, $\epsilon$, $|\delta'| < 1$ and $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 |\candidateset|})})$, the dilation property holds:

\begin{equation*}
\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = c]
\leq
e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = e^{\lambda} c] + \frac{\delta'}{2},
\end{equation*}
where the sensitivity in mechanism is still smooth sensitivity as above.

More specifically, in Beta-binomial system it is enough to take $\beta \leq \ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$.
\end{lem}

\begin{proof}
Based on Theorem \ref{thm_hellinegr_equality_beta} and \ref{thm_candidate_divide}, we use the same partition of $\candidateset$, $R_1, R_2$. It is enough to proof under just one partition. Without loss of generalization, we take $R_1$.

The sensitivity is always greater than 0, and our utility function $-\hellinger(\bysinfer(\dataobs),z)$ is smaller than zero, i.e., $u(z,\dataobs) \leq 0$, we need to consider two cases where $\lambda < 0$, and $\lambda > 0$:

We set the $h(c) = Pr[u(\hexpmech(\dataobs)) = c] = \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{NL(\dataobs)}$.

We first consider $\lambda < 0$. In this case, $1 < e ^ {\lambda}$, so the ratio $\frac{h(c)}{h(e^{\lambda}c)} = \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{exp(\frac{\epsilon (c \cdot e^{\lambda})}{2 S(\dataobs)})}$ is at most $\frac{\epsilon}{2}$.

Next, we proof the dilation property for $\lambda > 0$, The ratio of $\frac{h(c)}{h(e^{\lambda}c)}$ is $\exp(\frac{\epsilon}{2} \cdot \frac{u(\hexpmech(\dataobs)) (1 - e^{\lambda})}{S(\dataobs)})$. Consider the event $G = \{ \hexpmech(\dataobs) : u(\hexpmech(\dataobs)) \leq \frac{S(\dataobs)}{(1 - e^{\lambda})}\}$. Under this event, the log-ratio above is at most $\frac{\epsilon}{2}$. The probability of $G$ under density $h(c)$ is $1 - \frac{\delta'}{2}$. Thus, the probability of a given event $z$ is at most $Pr[c \cap G] + Pr[\overline{G}] \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c \cap G] + \frac{\delta'}{2} \leq e^{\frac{\epsilon}{2}} Pr[e^{\lambda}c] + \frac{\delta'}{2}$.\\

\textbf{Detail proof:}
	To show:
	\begin{equation*}
	\underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,\dataobs) = c]
	\leq
	e^{\frac{\epsilon}{2}} \underset{z \thicksim \hexpmech(\dataobs)}{Pr}[u(z,x) = e^{\lambda} c] + \frac{\delta'}{2},
	\end{equation*}
	for $z \in R_1$.

	Let $Pr[u(\hexpmech(\dataobs)) = c] = \frac{exp(\frac{\epsilon c}{2 S(\dataobs)})}{NL(\dataobs)}$ and $Pr[u(\hexpmech(\dataobs)) = e^{\lambda} c] = \frac{exp(\frac{\epsilon e^{\lambda} c}{2 S(\dataobs)})}{NL(\dataobs)}$ by definition.

>>>>

\author[*]{Jiawen Liu}
\author[**]{Mark Bun}
\author[*]{Gian Pietro Farina}
\author[*]{Marco Gaboardi}
\affil[*]{University at Buffalo, SUNY. \{jliu223,gianpiet,gaboardi\}@buffalo.edu}
\affil[**]{Princeton University. {mbun@cs.princeton.edu}}
\date{}
\maketitle
{\small \tableofcontents}

\newpage
\begin{abstract} Bayesian inference is a statistical method which
allows one to derive a \emph{posterior} distribution,
starting from a \emph{prior} distribution and observed data. Several
approaches have been explored in order to make this process differentially
private. For example, \cite{dimitrakakis2014robust}, and
\cite{wang2015privacy} proved that, under specific conditions, sampling from
the posterior distribution is already differentially private. \cite{zhang2016differential}, \cite{foulds2016theory},
designed differentially private mechanisms that output a
representation of the full posterior distribution.

When the output of a differentially private mechanism is a probability
distribution, accuracy is naturally measured by means of
\emph{probabilistic distances} measuring how far this distribution is
from the original one. Some classical examples are total variation distance,
Hellinger distance, $\chi^2$-distance, KL-divergence, etc.

In this work, we design a mechanism for
bayesian inference exploring the idea of calibrating noise using the
same probabilistic distance we want to measure accuracy with. 
We focus on two discrete models, the Beta-Binomial and the
Dirichlet-multinomial models, and one probability distance, Hellinger distance. 
Our mechanism can be understood as a version of  the exponential mechanism
where the noise is calibrated to the smooth sensitivity of the
utility function, rather than to its global sensitivity. In our
setting, the utility function is the probability distance we want to
use to measure accuracy. To show the usefulness of this mechanism we
show an experimental analysis comparing it with mechanisms based on
the Laplace mechanism.
\end{abstract}
 % TODO: replace with your keywords

\section{Introduction}
\label{sec_intro}
Data analysis techniques are broadly used in various applications in different areas to improve their services, including disease-medicine service, financial service, location service, social network and so on. In order to provide a better service, large of data are collected from users for analysis. As a consequence, the data privacy came to be a critical issue. Sensitivity information in data can be revealed through the analysis results. The key challenge here is to release a private analysis results, from which adversary cannot observe individual's sensitive information in data.

Plenty of work have been developed to solve this issue, guaranteeing the privacy in specific data analysis algorithms. They achieved the $\epsilon-$differential privacy by adopting either Laplace mechanism or achieved the $(\epsilon, \delta)-$differential privacy. But they are not giving better accuracy than the differential privacy mechanism itself. Here, we are proposing mechanism with better accuracy.

Our work is conducted under a Bayesian inference scenario, where the posterior distribution is the analysis result we obtained from the data.
Publishing the posterior distribution inferred from a sensitive dataset can
leak information about the individuals in the dataset.
In order to guarantee differential privacy and to protect the
individuals' data we can add noise to the posterior before releasing it.
The amount of the noise that we need to introduced
depends on the privacy parameter $\epsilon$ and the sensitivity of the inference to
small changes in the data set. 
Sensitivity can be computed in many different ways based on which metric space
we consider on the output set of the mechanism. In the literature on private Bayesian
inference (\cite{zhang2016differential,xiao2012bayesian}), it is only measured with
respect to the vector of numbers parametrizing the output distribution using, e.g. the $\ell_1$ norm.
A more natural approach which we explore here, is to measure sensitivity with respect to a metric on the space of inferred probability distributions.
A re-loved question is that of how to measure accuracy. Again,
this can be answered in different ways based on the metric imposed on the output space, and yet again
only in few works in literature (e.g. \cite{zhang2016differential})
distances between probability measures have been used for these purposes.

The question that this work aims at answering is whether
an approach based on probability metrics can improve on the accuracy of approaches based on metrics over
the numeric parameters of the distributions. 
We will see that in some cases this can happen.

\noindent \textbf{Main contributions.}
\begin{itemize}
  \item We designed a differentially private Bayesian inference mechanism based on the standard exponential mechanism.

  \item The accuracy is improved by two ways: 1) calibrating noise to the sensitivity of a metric over distributions (e.g. Hellinger distance ($\hellinger$), $f$-divergences, etc\dots). 2) Using a smooth upper bound on the local sensitivity and scale the noise to this smooth bound rather than global sensitivity, to improve the mechanism accuracy.

  \item A full proof on applying exponential mechanism to the smooth sensitivity is $(\epsilon, \delta)-$differential privacy is given in paper.

  \item We implemented the new proposed mechanism and other art-of-state mechanisms, comparing the performance in terms of accuracy and efficiency.
\end{itemize}

\noindent \textbf{Related Work.}

A plentiful of data analysis algorithms have been studied to preserve differential privacy, including the subspace clustering algorithm \cite{wang2015differentially}, the gradient decedent algorithm in deep learning \cite{abadi2016deep}, logical regression \cite{chaudhuri2009privacy}, principle component analysis \cite{chaudhuri2012near}, probabilitic inference \cite{williams2010probabilistic} and convergence in statistic estimation \cite{chaudhuri2012convergence}, etc.

In Bayesian Inference data analysis, mechanisms are proposed corresponded to maintain their differential privacy, focusing on 3 different goals: 1) Inherited differential privacy property of posterior sampling in Bayesian inference. \cite{dimitrakakis2014robust}, \cite{zhang2016differential}, \cite{zheng2015differential} and \cite{wang2015privacy}. 2) Data sampled and released from posterior distribution of Bayesian is differentially private \cite{Zhang2017privbayes}, \cite{dimitrakakis2015differential},  \cite{foulds2016theory}. 3) The inference process is differentially private and the posterior distribution released should be private itself, in the meantime, with good accuracy. The third topic where our work focus on is still very new.

\section{Preliminaries}
\label{sec_background}

@@

\noindent \textbf{Differential Privacy.} 
\begin{definition}
\label{def_epsilon_dp}
$\epsilon-$differential privacy.

A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any adjacent\footnote{Given $\dataobs, \dataobs'$  we say that $\dataobs$ and $\dataobs'$ are adjacent and we write, $\adj{\dataobs}{\dataobs'}$, iff\\
$\displaystyle \sum_{i}^{n}\iverson{x_i = x'_i }\leq 1$. } input $\dataobs, \dataobs' \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
\begin{equation*}
\Pr[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \Pr[H(\mathcal{M}(\dataobs')) \in B].
\end{equation*}

@@

\begin{definition}
\label{def_epsilon_delta_dp}
$(\epsilon,\delta)-$differential privacy.

A randomized mechanism $\mathcal{M}: \mathcal{X} \rightarrow \mathcal{Y}$ is differential privacy, iff for any $\adj{\dataobs}{\dataobs'} \in \mathcal{X}$, a metric $H$ over $\mathcal{Y}$ and a $B \subseteq H(\mathcal{Y})$, $\mathcal{M}$ satisfies:
\begin{equation*}
\Pr[H(\mathcal{M}(\dataobs)) \in B] = e^\epsilon \Pr[H(\mathcal{M}(\dataobs')) \in B] + \delta.
\end{equation*} 
\end{definition}

@@

\section{Mechanism Proposition}
\label{sec_mechs}
Given a prior distribution $\bprior=\betad(\alpha, \beta)$ and a sequence of $n$ observations $\dataobs\in\{0,1\}^n$, we define the follwing set:
\[
  \candidateset\equiv\{\betad(\alpha',\beta')\mid \alpha'=\alpha+\Delta\alpha, \beta'=\beta+n-\Delta\alpha\},
\]
where $\Delta\alpha$ is as defined in Section\ref{sec_background}.
Notice that $\candidateset$ has $n + 1$ elements, and
the Bayesian Inference process will produce an element from $\candidateset$
that we denote by $\bysinfer(\dataobs)$ -- we don't explicitly
parametrize the result by the prior, which from now on we consider
fixed and we denote it by $\bprior$.

\subsection{Baseline Mechanisms}
\label{subsec_baselines}
Baseline Mechanisms are introduced in prior to our mechanism: $\hexpmech$.

\subsubsection{Exponential Mechanism}
Exponential mechanism $\expmech{}{x}{u}{\candidateset}$ samples a element from the candidate set $\candidateset = \{r_1, r_2, \cdots r_n\}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 GS})$:
\begin{equation*}
\underset{z \thicksim \expmech{}{x}{u}{\candidateset} }{Pr}[z=r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 GS})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 GS})},
\end{equation*}
where $u(x,r)$ is the Hellinger scoring function over candidates, $-\hellinger(\bysinfer(\dataobs), r)$, and $GS$ is the global sensitivity calculated by:
\begin{equation*}
GS = 
\max_{\{|\dataobs,\dataobs'| \leq 1;\dataobs,\dataobs'\in \mathcal{X}^n\}}\max_{\{r\in \mathcal{R}\}}
|\hellinger(\bysinfer(\dataobs), r) - \hellinger(\bysinfer(\dataobs'), r)|
\end{equation*}

Exponential mechanism is $\epsilon -$differential privacy\cite{dwork2014algorithmic}.

\subsubsection{Exponential Mechanism with Local Sensitivity}
\label{subsec_emls}
% \subsubsection{Mechanism Set up}
Exponential mechanism with local sensitivity $\expmech{local}{x}{u}{\candidateset}$ share the same candidate set and utility function as it with standard exponential mechanism. This outputs a candidate $r \in \mathcal{R}$ with probability proportional to $exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})$:
\begin{equation*}
\underset{z \thicksim \expmech{local}{x}{u}{\candidateset}}{\Pr}[z=r] = \frac
{exp(\frac{\epsilon u(x,r)}{2 LS(\dataobs)})}
{\Sigma_{r' \in \mathcal{R}}\ exp(\frac{\epsilon u(x,r')}{2 LS(\dataobs)})},
\end{equation*}

where $LS(\dataobs)$ is the local sensitivity calculated by:

\begin{equation*}
LS(\dataobs)=\max_{\dataobs' \in \datauni^n:\adj{\dataobs}{\dataobs'}, r\in \mathcal{R}}\lvert \hellinger(\bysinfer(\dataobs'), r) - \hellinger(\bysinfer(\dataobs'), r)\rvert.
\end{equation*}

The exponential mechanism with local sensitivity is non-differential privacy\cite{dwork2014algorithmic}.

\subsubsection{Laplace Mechanism}
 Adding noise to the posterior distribution parameters directly, through Laplace mechanism ($\lap{\cdot}{\cdot}$) with post-processing:

 \[
 \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
 \] 
 where $Y \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Beta-binomial model; and
 \[
 \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
 \]
 where $Y_i \thicksim \lap{0}{\frac{\Delta \bysinfer}{\epsilon}}$ in Dirichlet-multinomial model. $\lfloor \cdot \rfloor^n_0$ is taking the floor value and truncating into $[0,n]$ to make sure the noised posterior is valid.

 Then release it as the private posterior distribution.

 The sensitivity used in this baseline mechanism is:
 \[
 \Delta \bysinfer \equiv \max\limits_{\dataobs, \dataobs' \in \{0,1\}^{n}, ||\dataobs - \dataobs'||_1 \leq 1} ||\bysinfer(\dataobs) - \bysinfer(\dataobs')||_1,
 \]
 which is proportional to the dimensionality.

\subsubsection{Improved Laplace Mechanism}

 Noise added to posterior distribution parameters are scaled to smaller sensitivity in this improved Laplace mechanism. Because in terms of two adjacent data sets $\dataobs, \dataobs'$, their posterior distributions by Bayesian inference -- $\bysinfer(\dataobs), \bysinfer(\dataobs')$ -- which parameter differs at most in 2 dimensions even though extended to Dirichlet-multinomial mode, i.e., $\Delta \bysinfer \leq 2$.

 Then it is enough to use sensitivity $1$ in 2 dimensions and $2$ in higher dimensions:

 \[
 \betad(\alpha +  \lfloor{\Delta \alpha + Y}\rfloor^n_0,\beta + n - \lfloor{\Delta \alpha + Y}\rfloor^n_0),
 \]
 where $Y \thicksim \lap{0}{\frac{1}{\epsilon}}$ in Beta-binomial model; and
 \[
 \dirichlet(\alpha_1 +  \lfloor{\Delta \alpha_1 + Y_1}\rfloor^n_0, \cdots, \alpha_k + \lfloor n - \sum_{i = 1}^{k-1}\lfloor{\Delta \alpha_i + Y_i}\rfloor^n_0 \rfloor^n_0),
 \]
where $Y_i \thicksim \lap{0}{\frac{2}{\epsilon}}$ in Dirichlet-multinomial model.

Both Laplace mechanism and improved one are $\epsilon -$differential privacy\cite{dwork2014algorithmic}.

@@

\begin{definition}
\label{def_smoo}
The mechanism $\hexpmech(\dataobs)$ outputs a candidate $r \in \candidateset$ with probability
\begin{equation*}
\underset{z \thicksim \hexpmech}{\Pr}[z=r] = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r)}{2\cdot S(\dataobs)}\big)}
{\nomalizer{\dataobs}}.
\end{equation*}
where $S_\beta(\dataobs)$ is the smooth sensitivity of $\hellinger(\bysinfer(\dataobs),-)$, calculated by:

\begin{equation}
  \label{eq:smooth}
   S(\dataobs)=\max_{\dataobs' \in \{0,1\}^{n}}\bigg \{LS(\dataobs') \cdot e^{-\gamma\cdot d(\dataobs,\dataobs')}\bigg\},
\end{equation}
where $d$ is the Hamming distance between two datasets, and $\gamma$ is the smooth upper bound in smooth sensitivity.
\end{definition}

This mechanism is based on the standard exponential mechanism
\cite{talwar}, with $\candidateset$ as the range and
$\hellinger(\cdot,\cdot)$ as the scoring function. The difference is
that in this mechanism we don't calibrate the noise w.r.t. to the
global sensitivity of the scoring function but w.r.t. to the smooth
sensitivity $S(\dataobs)$ -- defined by \cite{nissim2007smooth}-- of
$\hellinger(\bysinfer(\dataobs), \cdot)$, where $LS(\dataobs')$ denotes the local
sensitivity at $\dataobs'$, of the scoring function used in our mechanism and  $\gamma$ is the smooth upper bound for smooth sensitivity.

@@

% By setting the $\gamma$ as $\ln(1 - \frac{\epsilon}{2 \ln (\frac{\delta'}{2 (n + 1)})})$, $\hexpmech$ is $(\epsilon, \delta) -$differentially private, where $\delta = \frac{e^{\frac{\epsilon}{2}} \delta'}{2}$.

@@

In what follows, let $ \ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset$, we first introduce Lemma \ref{lem_score_pro_eq} and \ref{lem_score_pro_convert}.

\begin{lem}
\label{lem_score_pro_eq}
  Given $\hexpmech(\dataobs)$ and arbitrary $r_1, r_2 \in \candidateset$, then following holds:
  $$
  \ux{r_1} = \ux{r_2} \iff \hexpmechPr{\dataobs}{z = r_1} = \hexpmechPr{\dataobs}{z = r_2}.
  $$  
\end{lem}
\begin{proof} of Lemma \ref{lem_score_pro_eq}.
\begin{itemize}
  \item $\implies$

  $\ux{r_1} = \ux{r_2}$

  Apply $\ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset$:\\
  $\implies \hellinger(\bysinfer(\dataobs), r_1) = \hellinger(\bysinfer(\dataobs), r_2)$. \\
  $\implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_1)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
  = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_2)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}$.

  Apply\ Definition\ \ref{def_smoo}:\\
  $\implies \hexpmechPr{\dataobs}{z = r_1} = \hexpmechPr{\dataobs}{z = r_2}$.

  \item $\impliedby$

  $\hexpmechPr{\dataobs}{z = r_1} = \hexpmechPr{\dataobs}{z = r_2} $

  Apply Definition \ref{def_smoo}:\\
  $\implies \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_1)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}} 
    = \frac {exp\big(\frac{-\epsilon\cdot\hellinger(\bysinfer(\dataobs),r_2)}{2\cdot S(\dataobs)}\big)}{\nomalizer{\dataobs}}$.\\
  $\implies  \hellinger(\bysinfer(\dataobs), r_1) = \hellinger(\bysinfer(\dataobs), r_2)$.

  Apply\ $\ux{r} = \hellinger(\bysinfer(\dataobs), r)$ for $r \in \candidateset$:
  $\implies \ux{r_1} = \ux{r_2}$.
